Plots

### 2023-06-26 Code/Plots.Rmd
Small changes

>>>>

```{r}
library(ggplot2)
means_df <- data.frame(variable = names(means), mean = means)

# Define the grouping of bars
groupings <- list(c("2019H", "2022H"), c("2019S", "2022S"), c("2019F", "2022F"))

# Convert variable to a factor with desired order
means_df$variable <- factor(means_df$variable, levels = unlist(groupings))

# Create the bar graph
ggplot(means_df, aes(x = variable, y = mean, color = variable)) +
  geom_bar(size = 3) +
  labs(y = "Mean Reaction Time", x = "") +
  scale_color_manual(values = c("sienna2", "tan", "sienna2", "tan", "sienna2", "tan")) +
  theme_minimal() +
  theme(legend.position = "none")
#ggsave(filename = "2019vs2022ScatterPlot.pdf", path = "../Manuscript", height = 4, width = 6)
```

```{r}
comp <- read.csv("../Data/2019vs2022.csv")
#"C:\Users\ofior\Documents\Thesis\Data\2019vs2022.csv"
colnames(comp) <- c("Athlete", "Country", "2019 Heats", "2019 Semifinals", "2019 Finals", "2022 Heats", "2022 Semifinals", "2022 Finals")
```

```{r}
comp <- comp[, -c(1,2)]
```
```{r}
library(tidyr)
library(ggplot2)
df_long <- tidyr::pivot_longer(comp, cols = everything(), names_to = "Column", values_to = "Time")

order <- c("2019 Heats", "2019 Semifinals", "2019 Finals", "2022 Heats", "2022 Semifinals", "2022 Finals")
#df_long$Event <- factor(df_long$Event, levels = order)
```
```{r}
comp_plot <- ggplot(df_long, aes(x = Column, y = Time)) +
  geom_point() +
  labs(y = "Time") +
  ylim(0.08, 0.22)
  theme_minimal()
ggsave(filename="Scatterplot2019vs2022.pdf", path = "../Manuscript", plot=comp_plot, height = 4, width = 6)
```
